---
title: "Main functions"
author: "Jose Pérez Cano"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## fars_map_state

This is the main function of this package, it plots each accident of some year into a map of the state you choose. To call it just write `fars_map_state(state.num, year)` where the number of a state can be searched in  [Wikipedia](https://en.wikipedia.org/wiki/List_of_U.S._state_abbreviations)

## Some maps

For instance, this would be the representation of the accidents in 2014 in the state of Florida

```{r echo=FALSE, fig.show='hold', fig.align='center'}
source("fars_functions.R")
fars_map_state(12, 2014)
```
And this of Texas in 2013 

```{r echo=FALSE, fig.align='center'}
source("fars_functions.R")
fars_map_state(48,2013)
```

##fars_summarize_years

This function is another way of visualizing the accidents, instead of plotting into a map it tells you how many there are per year and month. It just need a vector with the years.

##Examples

This will the summary of the years 2013 to 2015

```{r echo=FALSE}
source("fars_functions.R")
library(magrittr)
fars_summarize_years(2013:2015)
```


##Other functions

The other functions of the package such as `fars_read` or `make_filename` are just useful functions to the two above, they aren't the purpose of this package but you can use if you want to access the data and modify it yourself. 


